### 2012-12-19 Docs/managing_jobs/managingjobs.tex
add more notes about running

The submission script {\tt jaguar.run} and shell script
{\tt process.jaguar} in {\tt wdconvect/job\_scripts/}
are designed to allow you to run \maestro\ with minimal interaction,
while being assured that the data is archived to HPSS on the NCCS
machines.

@@

Analogous scripts exist for running on Atlas, with the same general
procedure.  The command to chain a job on atlas is:
\begin{verbatim}
msub -l depend=<JOB-ID> <MSUB SCRIPT>
\end{verbatim}
where, again, {\tt <JOB-ID>} is the id number of the job that must
complete before the current submission runs and {\tt <MSUB SCRIPT>}
is the job submission script (e.g.\ {\tt atlas.run}).

@@

>>>>

The submission script {\tt jaguar.run} and shell script
{\tt process.jaguar} in {\tt Util/job\_scripts/jaguar/}
are designed to allow you to run \maestro\ with minimal interaction,
while being assured that the data is archived to HPSS on the NCCS
machines.

@@

The {\tt chainsub.sh} script can be used to automatically launch a number
of jobs depending on a single, currently queued (or running) job.

@@

The same set of submission scripts are available for hopper at NERSC in 
{\tt Util/job\_scripts/hopper/}.  They are mostly identical, with a few
minor changes for the local system configuration.  The use is the same
as described above.
